\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

%SetFonts

%SetFonts


\title{Methodology Asevdiversity}
\author{Lizzie Wolkovich and Christophe Rouleau-Desrochers}
\date{\today}

\begin{document}
\maketitle
\section{Steps}
\subsection{Step 1 – Subset of papers}
We conducted a literature search for papers that explored experiments on rootstock x scion interactions in grapevines. Using an ISI search with the query "rootstock* AND scion* AND grape*, we initially retrieved 530 references. From those, we randomly selected 140 articles. We scrutinized these articles to determine their relevance to our research, noting their provenance and the number of rootstocks and scions employed in each experiment. Some of the selected articles featured species other than grapes (e.g., grapefruit, kiwis), and a few were inaccessible. We subsequently excluded these articles from our dataset.

\subsection{Step 2 – Data scraping}

We proceeded to identify and record the geographical locations where each study was conducted. If the location was given in hour/degree/minutes, we converted it in decimals to ensure consistency. In cases where explicit coordinates were absent, we derived decimal coordinates based on the most precise location information available. If the study mentioned the name of the vineyard or campus where the experiment occurred, we used those location details. When no location was given, we estimated the location based on first author’s affiliation. The method used for location determination is in \emph{how} column of rootstockscionlatlon spreadsheet. 

Additionally, some of the papers retrieved from the ISI search were review articles. For these, we extracted relevant data if it was explicitly presented within the article In instances where certain information was missing, we conducted further searches to locate and include the specific studies mentioned in the review paper. We documented the ID number of the review paper that led us to the referenced article in the \emph{source\_paper\_id} column within the rootstockscionlatlon spreadsheet.

\subsection{Step 3 – Mapping rootstocks / scion data}
Subsequently, we determined the number of rootstocks and scions utilized in each experiment. When the data was available, we noted how many of each were used. Then using Plotly package in R, we created a choropleth map where the color gradient corresponds to the number of articles investigating rootstock x scion interactions in each country. We also adjusted the size gradient of the data points to reflect the number of rootstock varieties used in each study. The interactive version (HTML) was all created in R and the static version (SVG) was partially created in R. A second legend displaying the meaning of the dot sizes was created in Adobe Illustrator.

\section{Data Table, Image, and Other Data Details}
\subsection{Other entity 2}
\textbf{choropleth\_script.R}

Description:
Code, to create a choropleth map of rootstock x scion studies across the world. =
\subsection{Other entity 2}
\textbf{isi5May2023.bib}

Description:
Isi return of all 530 references
\subsection{Other entity 3}
\textbf{rootstockscionlatlon.csv}

Description:
Rootstock x scion interaction data set in which locations and rootstock and scion numbers were extracted.



\end{document}

